Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2021-02-15 05_calibration_data.Rmd
add some explanation for summary vars

An indicator of individual residence at or near a position can be useful when attempting to identify residence patches. Positions can be filtered on a metric such as residence time [@bracis2018].

@@

>>>>

First, we filter data where we know the animal spent some time at or near a position, as this is the first step to identify residence patches. 
One way of doing this is to filter out positions with speeds above which the animal is likely to be in transit, but a better way of doing this by filtering on a metric such as residence time [@bracis2018].

@@

### A note on summary statistics {-}

Users specifying a `summary_variable` should make sure that the variable for which they want a summary statistic is present in the data.
For instance, requesting mean speed by passing `summary_variable = "speed"` and `summary_function = "mean"` to `atl_res_patch`, should make sure that their data includes a column called `speed`.
